A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-17 paper.tex
Restructured figure scripts, put all figures on same range, first complete draft of section V

\begin{abstract}
Lightweight Temporal Compression
(LTC~\cite{schoellhammer2004lightweight}) is among the stream
compression method that provides the highest compression rate for the
lowest resource (CPU, RAM) consumption. As such, it makes it a very
good candidate for the compression of data streams acquired in
embedded, low-power systems such as connected
objects, systems on module (SoMs), etc The type of data acquired on
such systems, however, is often multi-dimensional. For instance
accelerometers and gyroscopes usually measure variables along 3
directions, these variables being distinct but related through the
actual movement of the sensor. In this paper, we investigate the
extension of LTC to higher dimensions. First, we provide a formulation of the algorithm
in an arbitrary vectorial space of dimension $n$. Furthermore, we
implement the algorithm for the infinity and Euclidean norms, in spaces of
dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC
to the 1-dimensional version, on gyroscopic data acquired on a SoM
device.
\end{abstract}

@@

@@

As mentioned before, norm selection in $\mathbb{R}^n$ has a critical
impact on the compression error and ratio. To appreciate this effect,
let us consider the comparison between the infinity norm and the
Euclidean norm in dimension 2. By comparing the unit disk to the unit
square, we obtain that the compression ratio of a random stream would
be $\frac{4}{\pi}$ times larger with the infinity norm than with the
Euclidean norm. Conversely, a compression error bounded by $\epsilon$
with the infinity norm corresponds to a compression error of
$\frac{\epsilon}{\sqrt{n}}$ with the Euclidean norm. Unsurprisingly, the
infinity norm is more 'tolerant' than the Euclidean norm.

@@

As reference above, the norm selection is importance. In this section,
we show the implementation of infinity norm and Euclidean norm.

%~ In practice, It's needed to transmit raw data which has multi-parameters
%~ to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
%~ Most of previous paper just force on single dimension sensor
%~ data Compression. So we purpose a method to compress multi-dimensional
%~ sensor data named LTC-D. It is used as linear estimation method.
%~ Same as usual estimation compression method,  distance(different)
%~ with compressed data from LTC-D and original data would not exceed
%~ the predefined error range. We need to find line to represent
%~ original data, it means the lines pass through datas' error range.
%~ But in stream data, time seires data, it is difficult, because
%~ all data do not show in same time plane. So this method will
%~ mapping all data into one time plane. Then for each mapped error
%~ range of data, check if there is intersection among them. If so means
%~ there is a line could represent original data, and vice versa.
\subsection{Multidimensional LTC with Manhattan distance}
In section 2, we can know that the repersentation of intersection
is a rectangular cuboid. So only one bounding box with n-dimensional
is needed to represent the intersection. Assume a bounding box
$\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
$i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
would be updated when this formular return true.
Otherwise return false.
\begin{enumerate}
    \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
    \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
            defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
            \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
    \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
            $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
    \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
            \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
    \item Otherwise, the intersection do not be empty. Updating
            the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
            each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
            \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
\end{enumerate}

% The method as below: assume the stream $i_{th}$ data
% $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
% be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
% As usual, the timestamp after basepoint would be set as mapping plane.
% We also need to record the intersect $S$ for find result lines.
% The first data $D_1$ would change into tolerance range $R_1$.
% initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
% into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
% and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
% on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
% with S, if there is overlap, update S = S intersect R_i. If not, the base point
% would be transmited and select a point in S as base point with timestamp $t_{i-1}$.

% \todo{refector}
% At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
% \begin{enumerate}
%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point. Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
%   \item Goto 2.
%   \item output \textit{z} data point.
%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
%   \item Goto 2.
%   \item After all, output \textit{z} data point and center of bounding box respectively.
% \end{enumerate}

According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively. Since, the intersection would be rectangle in 2D and cube in 3D, the corresponding max errors are $\frac{\epsilon}{\sqrt{2}}$ and $\frac{\epsilon}{\sqrt{3}}$. As we mentioned in Section 2, the infinity norm is more 'tolerant' than Euclidean norm. The max error between original data and reconstructed data certainly not greater than $\frac{\epsilon}{\sqrt{n}}$ where $n$ is dimension of data.
% for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
% If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
% But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
\todo{maybe need a graphic}

% In practice, Multidimensional LTC is same as implementing LTC in each
% parameter respectively. But we did some changes in our method. Assume
% $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with
% n-dimension, and a base data point Z  $(z_{1}, z_{2}, ...,
% z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming
% data to $t_1$ time-stamp and create a bounding box for recording
% overlapping range which includes upper and lower bound for each
% dimension base on $t_1$. cause the time different between two adjacent
% data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j +
% \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
% After that updating tolerance range by adding designed error margin
% which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}},
% j={1...n}$ with Manhattan distance. checking if there is overlap
% between tolerance and bounding box.The algorithm is as follows.

% At beginning of the algorithm, we need a base point (which we will call
% \textit{z}) and bounding box which has upper and lower bound for each
% parameter respectively.Then start the algorithm.
% \begin{enumerate}
%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point. Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
%   \item Goto 2.
%   \item output \textit{z} data point.
%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
%   \item Goto 2.
%   \item After all, output \textit{z} data point and center of bounding box respectively.
% \end{enumerate}

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidea norm, the representation of intersection is
volume. There is no specific model to record repersentation
with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
is needed. In order to test weather a set of balls intersect,
the Helly's theorem could work, but the complexity of
this method is too high to work with embeded, low-power
systems which has limited CPU and RAM resource. So we
implement Euclidean norm by using a method which based
on plane sweep and binary search. Assume the list of balls $S_{m-1}$ contains balls from $\mathcal{B}_1$ to $\mathcal{B}_{m-1}$, and an temporary data point $output$ used for updated origin $(\tau^k, \xi^k)$. From the formula (1) in Section 3, the $(\mathcal{B}_j)_{j \in \llbracket 1, {m-1} \rrbracket}$ is a sequence of decreasing radius, so the larger balls that includes new coming ball $\mathcal{B}_{m-1}$ could be reomved from list $S_{m-1}$ so that reducing processing complexity of method. Therefore the list $S_{m-1}$ may not includes $m-1$ balls. Assume each $\Hat{\mathcal{B}} \in S$ which has corresponding center $\Hat{z}$ and radius $\Hat{\epsilon}$.
Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$. The $\mathcal{B}_{m}$ should be one n-ball with center $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$. The method is written in Algorithm~\ref{algo:isThereIntersection}.

\begin{algorithm}
    \begin{flushleft}
        \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
        \textbf{Output:} $true|false$\\
    \end{flushleft}
    \begin{algorithmic}[1]
        \State d = n \Comment{dimension index}
        \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
        \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
        \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
            \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
                \State \textbf{return} false
            \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
                \State remove $\Hat{\mathcal{B}}$ from $S$
                \State \textbf{continue}\\
            $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
            $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
            \EndIf
        \EndFor
        \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
        \If{$max_d < min_d$}
            \State \textbf{return} false
        \EndIf
        \State temp\_output = output \Comment{used for next operation}
        \If{Recursive$(min_d, max_d, n, p\_cp)$}
            \State $output = temp\_output$
            \State \textbf{return} true
        \Else
            \State \textbf{return} false
        \EndIf
    \end{algorithmic}
    \caption{isThereIntersection}
    \label{algo:isThereIntersection}
\end{algorithm}

% \begin{enumerate}
%     \item Initialzation: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
%     \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
%             defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
%             \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
%     \item The $\mathcal{B}_{m}$ should be one n-ball with center
%             $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
%     \item For each ball $\hat{\mathcal{B}}$ in list $S$, if $\hat{\mathcal{B}} \bigcap \mathcal{B}_m = \O$, return False. Else if
%     $\mathcal{B}_m\subset\hat{\mathcal{B}}$, remove $\hat{\mathcal{B}}$ from list $S$.
%     \item Select parameter p = n (which is ball's dimension), define $Max_{(p=n)} = \min_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} + \frac{v_1}{v_j}\epsilon)}$, and $Min_{(p=n)} = \max_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} - \frac{v_1}{v_j}\epsilon)}$. If $Max_{(p=n)} < Min_{(p=n)}$, return False.
%     \item Use binary search to select $mid_{(p=n)} = (Min_{(p=n)} + Max_{(p=n)})/2$
% \end{enumerate}

% In Euclidean distance version, we also map the coming data into same
% time-stamp $t_1$ the timestamp after base point. The difference with
% Manhattan distance version is that recording overlapping part with
% a post-designed model is difficult, which need retain several arcs in
% 2-dimension, or convex surfaces in 3-dimension. In our method, we will
% record all tolerance range for every mapped data which come from base
% data point until coming data point, in order to checking if there is
% intersection among them. For instance, in 3D-t, assume we have a the
% base point $Z = D_0$ and the tolerance range $R_1$ which is a ball
% as the intersection S. we need a list L to record mapped balls
% from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping
% this data into $t_1$, and add it into list. Then the work is check out
% if all balls intersect, and form a public intersection.
% The method is based on plane sweep and binary search. At first, select one parameter,
% such as x-axis, finding a bounding range of all balls $B_i$ in x-axis.
% suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and
% $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap
% among balls, then the axis of the points inside intersection must located
% between Min_bound_x and Max_bound_x.
In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension. If the max value bigger than min value, then there is no intersection. After that. In Recursive function Algorithm~\ref{algo:recursive}, using binary search select
median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$. If bound range of dimension $d-1$ is not empty, continue calling function \textbf{Recursive}($min_{d-1}$, $min_{d-1}$, $d-1$, $temp\_output$). Recursively calling this function, until getting result.
\todo{add recursive pseudo-code}
% Using binary search to select
% mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding
% with the plane x = mid_x. If the get bounding range in y-axis where
% $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y,
% It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y,
% parallels z-axis, could pass through all balls. Finally, in z-axis,
% computing bounding range, and If $Max_bound_z > Min_bound_z$, there
% must be one or more points inside all balls. The problem be solved.
% If the loop of binary search in x-axis overs, then there is no public
% intersection among balls, and need to transmit and update base point.
% In this method we need O(n*logn*logn) time complexity for binary search
% in x-axis and y-axis and traversal all balls in z-axis, also O(n) space
% complexity is needed for maintaining list. According this method,
% it could be extended into N-dimensional data. The main idea is to search,
% dimension by dimension, from a room or plane or line and get intersection
% point finally.

% \todo{below content is useful? }
% In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
% \begin{itemize}
% \item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
% \item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
% \end{itemize}

% At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.

% \begin{algorithm}
%     \caption{whether disks intersect}
%     \begin{flushleft}
%         \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
%         \textbf{Output:} $true|false$  is there a intersection\\
%         \textbf{function} isIntersect$(l, d, p)$
%     \end{flushleft}
%     \begin{algorithmic}[1]
%         \State $tmp_list \gets null$
%         \State $max\_x\gets d.x+d.r$
%         \State $min\_x\gets d.x-d.r$

%         \ForAll{$old\_disk$ \textbf{in} $l$}
%             \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
%                 \State \textbf{return} false
%             \ElsIf{$d \cap old\_disk \neq d$}
%                 \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
%                         $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
%                         $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
%             \EndIf
%         \EndFor
%         \State $\textbf{add } d \textbf{ into } tmp\_list$
%         \If{$max\_x < min\_x$}
%             \State \textbf{return} false
%         \EndIf
%         \While{$min\_x \leqslant max\_x$}
%             \State $mid \gets (min\_x + max\_x)/2$
%             \State $max\_y \gets +\infty$
%             \State $min\_y \gets -\infty$
%             \For{$i=1$ \textbf{to} $tmp\_list.length$}
%                 \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
%                 \If{$P_1.y < max\_y$}
%                     \State $max\_y \gets p_1.y$
%                     \State $max\_index \gets i$
%                 \EndIf
%                 \If{$P_2.y > min\_y$}
%                     \State $min\_y \gets p_2.y$
%                     \State $min\_index \gets i$
%                 \EndIf
%             \EndFor
%             \If{$max\_y >= min\_y$}
%                 \State $p.x \gets mid$
%                 \State $p.y \gets (max\_y+min\_y)/2$
%                 \State $l \gets tmp\_list$
%                 \State \textbf{return} true
%             \EndIf
%             \State {Assume $P_d$ is the intersection between line of
%             centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
%             , and their common chord}
%             \If{$P_d.x < mid$}
%                 \State $max\_y \gets mid-1$
%             \ElsIf{$P_d.x > mid$}
%                 \State $min\_y \gets mid+1$
%             \EndIf
%         \EndWhile
%         \Return false
%     \end{algorithmic}
% \end{algorithm}

% The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk. It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks. Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$. In 3-dimension, It needs $O(\log^2\epsilon)$ to determine $mid\_3, mid\_2$, and $O(n)$ to traverse all balls in list and calculate bounding range of dimension d=1. So 3-dimensional method need $O(n \log^2\epsilon)$ totally. If we extend this idea for n-dimension, the complexiy of this method is $O(n \log^{n}\epsilon)$ where n is the number of dimension.

% \begin{algorithm}
%     \begin{flushleft}
%         \textbf{Input:} $S$, $\mathcal{B}_m$, $output$
%         \textbf{Output:} $true|false$  is there a intersection\\
%         \textbf{function} isIntersect$(l, o, p)$
%     \end{flushleft}
%     \begin{algorithmic}[1]
%         \State $tmp_list \gets null$
%         \State $max \gets o.d\_n+o.r$
%         \State $min \gets o.d\_n-o.r$

>>>>

\begin{abstract}
Lightweight Temporal Compression
(LTC~\cite{schoellhammer2004lightweight}) is among the stream
compression method that provides the highest compression rate for the
lowest resource (CPU, RAM) consumption. As such, it makes it a very
good candidate for the compression of data streams acquired in
embedded, low-power systems such as connected
objects, systems on module (SoMs), etc The type of data acquired on
such systems, however, is often multi-dimensional. For instance
accelerometers and gyroscopes usually measure variables along 3
directions, these variables being distinct but related through the
actual movement of the sensor. In this paper, we investigate the
extension of LTC to higher dimensions. First, we provide a formulation of the algorithm
in an arbitrary vectorial space of dimension $n$. Furthermore, we
implement the algorithm for the infinity and Euclidean norms, in spaces of
dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC
to the 1-dimensional version, on acceleration data acquired on a SoM
device.
\end{abstract}

@@

Compression reduces radio usage but increases resource usage.

@@

As mentioned before, norm selection in $\mathbb{R}^n$ has a critical
impact on the compression error and ratio. To appreciate this effect,
let us consider the comparison between the infinity norm and the
Euclidean norm in dimension 2. By comparing the unit disk to the unit
square, we obtain that the compression ratio of a random stream would
be $\frac{4}{\pi}$ times larger with the infinity norm than with the 
Euclidean norm. In 3D, this ratio would be $\frac{6}{\pi}$. Conversely, 
a compression error bounded by $\epsilon$ with the infinity norm 
corresponds to a compression error of $\frac{\epsilon}{\sqrt{n}}$ with 
the Euclidean norm. Unsurprisingly, the
infinity norm is more 'tolerant' than the Euclidean norm.

@@

%~ As reference above, the norm selection is importance. In this section,
%~ we show the implementation of infinity norm and Euclidean norm.

%~ \subsection{Multidimensional LTC with Manhattan distance}
%~ In section 2, we can know that the repersentation of intersection
%~ is a rectangular cuboid. So only one bounding box with n-dimensional
%~ is needed to represent the intersection. Assume a bounding box
%~ $\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
%~ has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
%~ $i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
%~ be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
%~ would be updated when this formular return true.
%~ Otherwise return false.
%~ \begin{enumerate}
    %~ \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
    %~ \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
            %~ defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
            %~ \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
    %~ \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
            %~ $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
    %~ \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
            %~ \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
    %~ \item Otherwise, the intersection do not be empty. Updating
            %~ the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
            %~ each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
            %~ \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
%~ \end{enumerate}

%~ According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively. Since, the intersection would be rectangle in 2D and cube in 3D, the corresponding max errors are $\frac{\epsilon}{\sqrt{2}}$ and $\frac{\epsilon}{\sqrt{3}}$. As we mentioned in Section 2, the infinity norm is more 'tolerant' than Euclidean norm. The max error between original data and reconstructed data certainly not greater than $\frac{\epsilon}{\sqrt{n}}$ where $n$ is dimension of data.

%~ \todo{maybe need a graphic}

%~ \subsection{Multidimensional LTC with Euclidean distance}
%~ In Euclidea norm, the representation of intersection is
%~ volume. There is no specific model to record repersentation
%~ with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
%~ is needed. In order to test weather a set of balls intersect,
%~ the Helly's theorem could work, but the complexity of
%~ this method is too high to work with embeded, low-power
%~ systems which has limited CPU and RAM resource. So we
%~ implement Euclidean norm by using a method which based
%~ on plane sweep and binary search. Assume the list of balls $S_{m-1}$ contains balls from $\mathcal{B}_1$ to $\mathcal{B}_{m-1}$, and an temporary data point $output$ used for updated origin $(\tau^k, \xi^k)$. From the formula (1) in Section 3, the $(\mathcal{B}_j)_{j \in \llbracket 1, {m-1} \rrbracket}$ is a sequence of decreasing radius, so the larger balls that includes new coming ball $\mathcal{B}_{m-1}$ could be reomved from list $S_{m-1}$ so that reducing processing complexity of method. Therefore the list $S_{m-1}$ may not includes $m-1$ balls. Assume each $\Hat{\mathcal{B}} \in S$ which has corresponding center $\Hat{z}$ and radius $\Hat{\epsilon}$.
%~ Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$. The $\mathcal{B}_{m}$ should be one n-ball with center $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$. The method is written in Algorithm~\ref{algo:isThereIntersection}.

%~ \begin{algorithm}
    %~ \begin{flushleft}
        %~ \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
        %~ \textbf{Output:} $true|false$\\
    %~ \end{flushleft}
    %~ \begin{algorithmic}[1]
        %~ \State d = n \Comment{dimension index}
        %~ \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
        %~ \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
        %~ \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
            %~ \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
                %~ \State \textbf{return} false
            %~ \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
                %~ \State remove $\Hat{\mathcal{B}}$ from $S$
                %~ \State \textbf{continue}\\
            %~ $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
            %~ $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
            %~ \EndIf
        %~ \EndFor
        %~ \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
        %~ \If{$max_d < min_d$}
            %~ \State \textbf{return} false
        %~ \EndIf
        %~ \State temp\_output = output \Comment{used for next operation}
        %~ \If{Recursive$(min_d, max_d, n, p\_cp)$}
            %~ \State $output = temp\_output$
            %~ \State \textbf{return} true
        %~ \Else
            %~ \State \textbf{return} false
        %~ \EndIf
    %~ \end{algorithmic}
    %~ \caption{isThereIntersection}
    %~ \label{algo:isThereIntersection}
%~ \end{algorithm}

%~ In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension. If the max value bigger than min value, then there is no intersection. After that. In Recursive function Algorithm~\ref{algo:recursive}, using binary search select
%~ median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$. If bound range of dimension $d-1$ is not empty, continue calling function \textbf{Recursive}($min_{d-1}$, $min_{d-1}$, $d-1$, $temp\_output$). Recursively calling this function, until getting result.
%~ \todo{add recursive pseudo-code}

%~ In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$. In 3-dimension, It needs $O(\log^2\epsilon)$ to determine $mid\_3, mid\_2$, and $O(n)$ to traverse all balls in list and calculate bounding range of dimension d=1. So 3-dimensional method need $O(n \log^2\epsilon)$ totally. If we extend this idea for n-dimension, the complexiy of this method is $O(n \log^{n}\epsilon)$ where n is the number of dimension.

%~ \begin{algorithm}
    %~ \begin{flushleft}
        %~ \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
    %~ \end{flushleft}
    %~ \begin{algorithmic}[1]
        %~ \While{$left \leqslant right$}
            %~ \State $mid \gets (left + right)/2$
            %~ \State $max \gets +\infty$
            %~ \State $min \gets -\infty$
            %~ \For{$i=1$ \textbf{to} $tmp\_list.length$}
                %~ \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
                %~ \If{$P_1.d_{j-1} < max$}
                    %~ \State $max \gets p_1.d_{j-1}$
                    %~ \State $max\_index \gets i$
                %~ \EndIf
                %~ \If{$P_2.d_{j-1} > min$}
                    %~ \State $min \gets p_2.d_{j-1}$
                    %~ \State $min\_index \gets i$
                %~ \EndIf
            %~ \EndFor
            %~ \If{$max >= min$}
                %~ \State $p.d_j \gets mid$
                %~ \If{Recursive$(min, max, j-1, p)$}
                    %~ \State \textbf{return} true
                %~ \EndIf
            %~ \EndIf
            %~ \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
            %~ \If{$P_d.d_j < mid$}
                %~ \State $right \gets mid-1$
            %~ \ElsIf{$P_d.d_j > mid$}
                %~ \State $left \gets mid+1$
            %~ \EndIf

        %~ \EndWhile
        %~ \Return false
    %~ \end{algorithmic}
%~ \end{algorithm}

\section{Experiments and Results}

We conducted two experiments using Motsai's Neblina 
module\footnote{\url{ https://motsai.com/products/neblina}}, a system 
with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
and Bluetooth Low Energy connectivity. The Neblina has a 3D 
accelerometer, a 3D gyroscope, a 3D magnetometer, and environmental sensors 
for humidity, temperature and pressure. It can function as an Inertial 
Motion Unit, a Vertical Reference Unit, or an Attitude and Heading 
Reference System. The Neblina has a battery of 100mAh; its average 
consumption is 2.52~mA without radio transmission and 3.47~mA with 
radio transmission, leading to an autonomy of 39.7~h without 
transmission and 28.8~h with transmission. \todo{Omid, could you review
this paragraph?}
